### 2017-09-27 TF-vldb2018/sec-intro.tex

\warn{To our knowledge, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting considered so far.}

>>>>

\warn{To our knowledge, no previous work studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting considered so far.
\looseness=-1
}
